Connected or Disconnected?

### 2022-11-18 Social Isolation in China.qmd
Move to Quarto

---
title: "Connected or Disconnected?"
subtitle: "An Examination of the Relationship between Social Media Use and Feelings of Isolation in China"
author: 
  - Jason Gainous^[Duke Kunshan University, jason.gainous@louisville.edu]
  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "The following brief paper is simply the preliminary results of our study. We seek to identify the relationship between social media use and feelings of isolationism in China. This study is based on original date. We conducted a nationwide survey of Chinese citizens conducted in 2015 measuring a range of concepts including those here. The preliminary results are promising. We develop an index of personal isolationism and model this as a function of social media use, connection to the outside digital world, and urbanicity, while controlling for a host of individual level factors. The results suggest the following: 1) Social media use does not have a generalized relationship with isolationism, 2) Those who use VPNs/proxy servers tend to feel less isolated than those who do not, 3) Those living in urban environments tend to feel more isolated, 3) There is a strong positive relationship between social media use and feelings of isolation for those who frequently use VPNs/proxy servers, and 4) The is a strong positive relationship between social media use and feelings of isolation for those living in rural China."
keywords: 
  - social isolation
  - social media
  - China
output: bookdown::html_document2
---

@@

kable(summarize(key.vars, type="numeric")) %>% 
  kable_styling()
```

@@

ggcorrplot(cors, title="Key variables associated with connectedness", lab=TRUE, type="lower")
```

>>>>

---
title: "Connected or Disconnected?"
author: 
  - Jason Gainous^[Duke Kunshan University, jason.gainous@louisville.edu]
  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "The following brief paper is simply the preliminary results of our study. We seek to identify the relationship between social media use and feelings of isolationism in China. This study is based on original date. We conducted a nationwide survey of Chinese citizens conducted in 2015 measuring a range of concepts including those here. The preliminary results are promising. We develop an index of personal isolationism and model this as a function of social media use, connection to the outside digital world, and urbanicity, while controlling for a host of individual level factors. The results suggest the following: 1) Social media use does not have a generalized relationship with isolationism, 2) Those who use VPNs/proxy servers tend to feel less isolated than those who do not, 3) Those living in urban environments tend to feel more isolated, 3) There is a strong positive relationship between social media use and feelings of isolation for those who frequently use VPNs/proxy servers, and 4) The is a strong positive relationship between social media use and feelings of isolation for those living in rural China."
keywords: 
  - social isolation
  - social media
  - China
format: pdf
editor: visual
---

@@

kable(summarize(key.vars, type="numeric")) %>% 
  kable_styling(latex_options="striped")
```

@@

ggcorrplot(cors, title="Key variables associated with connectedness", 
           lab=TRUE, type="lower", insig="blank")
```
